Estimating individual subjective values of emotion regulation strategies

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added BSCS scale

>>>>

*Self-Regulation Scale.*

*Brief Self-Control Scale.* 
As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] was used. 
It comprises 13 items (e.g., “I am good at resisting temptations”) with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me). 
The scale shows acceptable internal consistency (Cronbach’s $\alpha=.81$)[@Sproesser2011] .

*Baratt Impulsiveness Scale.*
